---
title: "Coding assignment"
author: "Ajla Dzajic"
date: "Friday, May 27, 2016"
output: pdf_document
---

### Data

For calculating the expected results we're provided with two input files, namely

1. **tickets_sold.csv** - each row contains the booking information for one individual ticket 

2. **row_capacity.csv** - each row contains the maximum capacity for an auditorium_row 

For simplicity, we assume that there is only one auditorium in the cinema that we are looking at.  


### Exected results

Our task is to calculate three different results, namely 

1. **Total_tickets_per_week_and_movie**

2. **Seat_load_factor_per_week_and_movie** 

3. **Seat_load_factor_per_week**


&nbsp;


```{r, warning=FALSE}
# dir.create("data_assignment")
# setwd("C:/Users/ajla/Documents/data_assignment")


row_capacity <- read.csv("assignment/row_capacity.csv", header = TRUE) 
tickets_sold <- read.csv("assignment/tickets_sold.csv", header = TRUE)

str(row_capacity)
str(tickets_sold)
```

&nbsp;

### Total_tickets_per_week_movie_row 

Aggregate the number of individual tickets per show.

```{r}
my_var <- tickets_sold[c("ticket_id", "movie", "calendarweek", "auditorium_row")]
head(my_var)
ft <- ftable(auditorium_row ~ calendarweek + movie, data = my_var)
ft
```

&nbsp;

### Seat_load_factor_per_week_movie_row

Divide the total tickets by the maximum capacity for that particular auditorium_row.

```{r}
for(i in 1:length(row_capacity$auditorium_row)){
        ft[, i] <- ft[, i]/row_capacity$max_seats_per_row[row_capacity$auditorium_row == i]
}
ft
```

&nbsp;

&nbsp;

&nbsp;

&nbsp;


### Seat_load_factor_per_week_row 
Use the average seat_load_factor over the individual shows per calendarweek.

```{r}
aggregate(Freq ~ calendarweek + auditorium_row, data = ft, FUN = mean)
```


&nbsp;

